COSC-373 Final Report: Bitcoin

### 2022-05-12 paper/paper.tex
Start cryptographic hash functions.

The main idea behind digital signatures is as follows. Both Alice and Bob each
generate a private/public key pair for themselves, where each key is a string of
bits and private keys are kept secret (i.e., only Alice knows her private key
and only Bob knows his private key). Producing a signature involves a function
$\mathsf{sign(msg, priKey)}$, which takes Alice's message $\mathsf{msg}$ and
private key $\mathsf{priKey}$ as inputs and outputs Alice's signature
$\mathsf{sig}$. Similarly, verifying the authenticity of the received message
involves a function $\mathsf{verify(msg, sig, pubKey)}$, which takes the
received message $\mathsf{msg}$, the signature $\mathsf{sig}$, and Alice's
public key $\mathsf{pubKey}$ as inputs and outputs \emph{true} if the signature
was produced using Alice's message and private key, and \emph{false} otherwise.
We will not discuss how the $\mathsf{sign()}$ and $\mathsf{verify()}$ functions
work in depth since such details are not the focus of this work.

@@

>>>>

The main idea behind digital signatures is as follows. Both Alice and Bob each
generate a \emph{private key} and \emph{public key} pair for themselves, where
each key is a array of bits and private keys are kept secret (i.e., only Alice
knows her private key and only Bob knows his private key). Producing a signature
involves a function $\mathsf{sign(msg, priKey)}$, which takes Alice's message
$\mathsf{msg}$ and private key $\mathsf{priKey}$ as inputs and outputs Alice's
signature $\mathsf{sig}$. Similarly, verifying the authenticity of the received
message involves a function $\mathsf{verify(msg, sig, pubKey)}$, which takes the
received message $\mathsf{msg}$, the signature $\mathsf{sig}$, and Alice's
public key $\mathsf{pubKey}$ as inputs and outputs \emph{true} if the signature
was produced using Alice's message and private key, and \emph{false} otherwise.
We will not discuss how the $\mathsf{sign()}$ and $\mathsf{verify()}$ functions
work in depth since such details are not the focus of this work.

@@

A \emph{cryptographic hash function} is a hash function that takes as input data
(i.e., a \emph{message}) of an arbitrary size and outputs a bit array (i.e.,
\emph{hash}) of a fixed size. In the case of the SHA256 cryptographic hash
function, the hash has a length of 256 bits.

Cryptographic hash functions ideally should have the following properties.
First, computing the hash of a given message should be quick. Second, generating
the message from only the hash should be computationally infeasible. Third,
finding two different messages that map to the same hash under the function
should also be infeasible. Fourth, slightly changing the message should change
the hash so much such that the old and new hashes seem uncorrelated.
